Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-28 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
finished out draft of results section, one round of corrections, some ideas for conclusions; first draft to PC

	\par The frequency of energy release in the solar corona is an important piece of evidence for determining the yet unknown coronal heating mechanism(s). However, measurement of the heating frequency, through both direct and indirect means, has proved challenging. With regard to the direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a supposed precursor to bursty energy release. Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing these $\mathrm{EM}$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}. Efforts to measure the heating frequency through intensity fluctuations in AR cores have proved similarly difficult \citep{ugarte-urra_determining_2014}.

@@

	\par We define our heating function in terms of a series of discrete heating events plus a static background heating to ensure that the loop does not drop to unphysically low temperatures and densities between events. Thus, for loop half-length $L$ and cross-sectional area $A$, for a triangular heating pulse of duration $\tau$, the total  event energy is $\varepsilon=LAH\tau/2$, where $H$ is the heating rate. Each run will consist of $N$ heating events, each with peak amplitude $H_i$, and a steady background value of $H_{bg}=3.5\times10^{-5}$ erg cm$^{-3}$ s$^{-1}$.

@@

		\caption{\textbf{Top}: uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$. The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $\langle t_N\rangle=2000$ s.}

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	\par We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $t_{total}=8\times10^4$ s and $\tau=200$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i=LA\tau H_i/2$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant, independent of $t_N$.

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim16$ events, meaning the events from a single run do not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied. Thus, when $t_N=5000$ s and $N\sim15$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and power-law case, $t_N,i=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ (blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event (green). Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.

@@

	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R\sim(t_N+200)/8$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the panels of \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the average over all $N_R$ curves. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.

@@

	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different. The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s. 

@@

	\par The $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em}, in which only the electrons are heated, evolve similarly to those shown in \autoref{fig:single_em}. This is particularly true on the cool side where the density is sufficiently high, allowing the electrons and the ions to equilibrate such that there is no discernible difference compared to the single-fluid case. On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar. However, for $t_N\ge1500$ s, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK. This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK. In the power-law cases, this feature is less pronounced and the $\mathrm{EM}(T)$ extends to slightly higher temperatures.

@@

	\par In \autoref{fig:ion_em} in which only the ions are heated, the cool side of the $\mathrm{EM}(T)$ is very similar to both the single-fluid and electron heating cases because the electron and ion populations are in equilibrium during this portion of the loop's evolution. On the hot side, for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power-law cases, the peak of the $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in \autoref{fig:single_em} and \autoref{fig:el_em}.

@@

	\par These few high energy events allow for $T\gg T_{max,0}$ in the case where the events are chosen from a power-law distribution(blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is already sufficiently dense due to the relatively short draining and cooling times, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ power-law case is an extended cool emission measure; the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical. This provides further evidence for these two portions of the emission measure distribution being largely independent as they are determined by separate phases of the loop evolution.

@@

	\par Another important discrepancy between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$. Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$. From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$. In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s. So even for the lowest heating frequency in the uniform case, the heating rate is still much lower. Furthermore, for low $t_N$, between each event the loop is allowed to drain to its equilibrium value (as determined by the background heating) such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff. On the other hand, when the heating events are selected from a power-law, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times), allowing the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively. We fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$. The left panel of \autoref{fig:em_slope_varying_bounds} shows the $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.

@@

	\par\citet{brosius_pervasive_2014}, using observations of an active region from the EUNIS-13 sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating. As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$. Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to the cool side. Here, we choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma. 

@@

	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$. We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same. Here we have not included the uniform heating case due to small number statistics (i.e. $<20$ emssion measure ratios). The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes. We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$. It seems that the value of the emission measure ratio is more sensitive to the heating frequency for $t_N>4000$ s.

>>>>

	\par The frequency of energy release in the solar corona is an important piece of evidence for determining the yet unknown coronal heating mechanism(s). However, measurement of the heating frequency, through both direct and indirect means, has proved challenging. With regard to direct evidence of reconnection-driven (DC) heating, only recently have observations provided sufficient resolution to resolve magnetic field braiding \citep{cirtain_energy_2013}, a possible precursor to bursty energy release. Additionally, while the resulting AR core emission measure distribution holds many clues as to how the coronal plasma is heated and cools, reconstructing $\mathrm{EM}(T)$ from spectroscropic and narrow-band observations is non-trivial, with differrent inversion methods often giving significantly different results \citep{landi_monte_2012,aschwanden_benchmark_2015}. Efforts to measure the heating frequency through intensity fluctuations in AR cores have proved similarly difficult \citep{ugarte-urra_determining_2014}.

@@

@@

		\caption{\textbf{Top}: Uniform heating amplitudes for $t_N=1000$ s; \textbf{Middle:} Uniform heating amplitudes for $t_N=5000$ s; \textbf{Bottom:} Heating amplitudes drawn from a power-law distribution with index $\alpha=-1.5$. The events shown in red have wait times that depend on the previous event energy while the events shown in blue have uniform wait times. The mean wait time in both cases is $t_N=2000$ s.}

@@

	\par We define our heating function in terms of a series of discrete heating events plus a static background heating to ensure that the loop does not drop to unphysically low temperatures and densities between events. For a triangular heating pulse of duration $\tau$ injected into a loop of half-length $L$ and cross-sectional area $A$, the total  event energy is $\varepsilon=LAH\tau/2$, where $H$ is the heating rate. Each model run will consist of $N$ heating events, each with peak amplitude $H_i$, and a steady background heating of $H_{bg}=3.5\times10^{-5}$ erg cm$^{-3}$ s$^{-1}$.
	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the time-averaged volumetric heating rate needed to kepp a loop of half-length $L=40$ Mm at $\bar{T}\approx4$ MK as  $H_{eq}\sim3.6\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	\par We define the heating frequency in terms of the waiting time, $t_N$, between successive heating events. Following \citet{cargill_active_2014}, the range of waiting times is $250\le t_N\le5000$ s in increments of 250 s, for a total of 20 different possible heating frequencies. Additionally, $t_N$ can be written as $t_N=(t_{total}-N\tau)/N$, where we fix $t_{total}=8\times10^4$ s and $\tau=200$ s. Note that because $t_{total}$ and $\tau$ are fixed, as $t_N$ increases, $N$ decreases. Correspondingly, $\varepsilon_i=LA\tau H_i/2$, the energy injected per event, increases according to \autoref{eq:heating_rate_constraint} such that the total energy injected per run is constant.

@@

	\par According to the nanoflare heating model of \citet{parker_nanoflares_1988}, turbulent loop footpoint motions twist and stress the field, leading to a buildup and subsequent release of energy. Following \citet{cargill_active_2014}, we let $\varepsilon_i\propto t_{N,i}^{\beta}$, where $\varepsilon_i,t_{N,i}$ are the total energy of event $i$ and waiting time following event $i$, respectively, and $\beta=1$ such that the event energy scales linearly with the waiting time. The reasoning for such an expression is as follows. Bursty, nanoflare heating is thought to arise from the stressing and subsequent relaxation of the coronal field. If a sufficient amount of energy is released into the loop, the field will need enough time to ``unravel'' and ``wind up'' again before the next event such that the subsequent waiting time is large. Conversely, if only a small amount of energy is released, the field will require a shorter unwinding time, resulting in a shorter interval between the subsequent events. Thus, this scaling provides a way to incorporate a more physically motivated heating function into a hydrodynamic model which cannot self-consistently determine the heat input based on the evolving magnetic field. \autoref{fig:heating_funcs} shows the various heating functions used for several example $t_N$ values.

@@

	\par We compute the peak heating rate per event in two different ways: 1) the heating rate is uniform such that $H_i=H_0$ for all $i$ and 2) $H_i$ is chosen from a power-law distribution with index $\alpha$ where $\alpha=-1.5,-2.0,$ or $-2.5$. For the second case, it should be noted that, when $t_N\approx5000$ s, $N\sim16$ events, meaning the events from a single run do not accurately represent the distribution of index $\alpha$. Thus, a sufficiently large number of runs, $N_{R}$, are computed for each $t_N$ to ensure that the total number of events is $N_{tot}=N\times N_{R}\sim10^4$ such that the distribution is well-represented. \autoref{fig:parameter_space} shows the parameter space we will explore. For each set of parameters and waiting time $t_N$, we compute the resulting emission measure distribution for $N$ events in a period $t_{total}$. This procedure is repeated $N_R$ times until $N\times N_R\sim10^4$ is satisfied. Thus, when $t_N=5000$ s and $N\sim16$, $N_R=625$, meaning the model is run 625 times with a heating frequency of $t_N=5000$ s in order to properly fill out the event energy distribution.

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$, that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution, $\mathrm{EM}(T_{eff})$.

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). In each 0D hydrodynamic simulation, a loop of half-length $L=40$ Mm is heated by $N$ triangular events of duration $\tau=200$ s and peak heating rate $H_i$ for a duration of $t_{total}=8\times10^4$ s. The average interval between subsequent events is $t_N$ (in the uniform and $\beta=0$ cases, $t_{N,i}=t_N$ exactly for all $i$). We focus primarily on the emission measure distribution, $\mathrm{EM}(T)$, and observables typically calculated from $\mathrm{EM}(T)$. In all cases, the coronal emission measure is calculated according to the method outlined in section 3 of \citetalias{barnes_inference_2016}. The corresponding NEI results, $\mathrm{EM}(T_{eff})$, are calculated similarly, but using $T_{eff}$ (see \autoref{subsec:nei}) instead of $T$. All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The solid lines in the two power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution. The standard deviation is not included in the NEI results.}

@@

	\par In our first set of results, we compare $\mathrm{EM}(T)$ for three different types of heating functions, across six different heating frequencies. \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} show the emission measure distributions in the single-fluid case, electron heating case, and ion heating case, respectively. Each panel in each figure corresponds to a different waiting time ($t_N$) and includes three different types of heating functions: uniform heating events (red), events chosen from a power-law distribution of index $\alpha=-2.5$ ($\beta=0$ case, blue), and events chosen from a power-law distribution of index $\alpha=-2.5$ where the time between successive events depends on the heating rate of the preceding event ($\beta=1$ case, green). Note that in all three figures, we show the results for only a single power-law index, $\alpha=2.5$. Furthermore, the dashed lines denote the corresponding NEI cases, $\mathrm{EM}(T_{eff})$.

@@

	\par Recall from \autoref{subsec:heating_stats} that for those heating functions which choose peak heating rates from a power-law distribution, for each $t_N$, we run the model $N_R$ times. Thus, for each point in our parameter space, we produce $N_R$ $\mathrm{EM}(T)$ curves. In order to present our results compactly, the solid lines in \autoref{fig:single_em}, \autoref{fig:el_em}, and \autoref{fig:ion_em} each show the mean $\mathrm{EM}(T)$ over all $N_R$ curves. The shading represents $1\sigma$ from the mean. In this way, we account for the variations that may occur because of a lack/excess of strong heating events due to limited sampling from the distribution.

@@

	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different. The uniform (red) and $\beta=0$ (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the $\beta=1$ curves (green) extend to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and $\beta=0$ cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. Contrastingly, on the hot side, the $\beta=0$ and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s. 

@@

	\par The $\mathrm{EM}(T)$ curves for the different types of heating functions shown in \autoref{fig:el_em}, in which only the electrons are heated, evolve similarly to those shown in \autoref{fig:single_em}. This is particularly true on the cool side where the density is sufficiently high, allowing the electrons and the ions to equilibrate such that there is no discernible difference compared to the single-fluid case. On the hot side, for $t_N\le750$ s, the electron and single-fluid cases are quite similar. However, for $t_N\ge1500$ s, in the electron heating case, $\mathrm{EM}(T)$ steepens just above 4 MK and then flattens out near 10 MK. This change in shape is most obvious in the uniform heating case where a distinct ``hot shoulder'' forms just above 10 MK. In the power-law cases, this feature is less pronounced though $\mathrm{EM}(T)$ extends to slightly higher temperatures.

@@

	\par In \autoref{fig:ion_em} in which only the ions are heated, the cool side of the $\mathrm{EM}(T)$ is very similar to both the single-fluid and electron heating cases because the electron and ion populations are in equilibrium during this portion of the loop's evolution. On the hot side, for intermediate to low heating frequencies (i.e. $t_N\ge1500$ s), the $\mathrm{EM}(T)$ in the uniform heating case is truncated below 10 MK and in the power-law cases extends to just above 10 MK for the lowest heating frequency ($t_N=5000$ s). This cutoff at lower temperatures is due to the fact that electrons cannot ``see'' the ions until they have cooled well below their peak temperature. This is discussed in \citetalias{barnes_inference_2016} though in the single-pulse cases, the cutoff occured at lower temperatures. Additionally, in both the uniform and power-law cases, the peak of $\mathrm{EM}(T)$ is wider for these low frequencies compared to those cases shown in the lower right panels of \autoref{fig:single_em} and \autoref{fig:el_em}.

@@

	\par These few high energy events allow for $T\gg T_{max,0}$ in the case where the events are chosen from a power-law distribution(blue and green curves) as seen in the middle panel of \autoref{fig:nT_sample_profiles}. Because these events are injected into a plasma that is already sufficiently dense due to the relatively short draining and cooling times, the emission measure is able to ``see'' these hot temperatures, resulting in a $>10$ MK component of $\mathrm{EM}(T)$ (see lower left panel of \autoref{fig:single_em} and \autoref{fig:el_em}). Contrastingly, in the uniform case, $T_{max,0}<10$ MK such that $\mathrm{EM}(T)$ has a steep cutoff right at 10 MK. Additionally, we note that the only effect of the longer wait times in the $\beta=1$ case as compared to the $\beta=0$ case is an extended cool emission measure at intermediation frequencies (e.g. $t_N=2500$ s); the hot part of $\mathrm{EM}(T)$ for both power-law cases is nearly identical. In this way, the hot and cool sides of the emission measure distribution are largely isolated from one another as they are determined by separate phases of the loop evolution.

@@

	\par Another important discrepancy between the uniform and power-law cases is the impact of NEI on the hot part of $\mathrm{EM}(T)$. Recall from \autoref{subsec:params} that the uniform heating rate $H_0=2t_{total}H_{eq}/N\tau=2H_{eq}(t_N/\tau+1)$. From the top panel of \autoref{fig:nT_sample_profiles} we see that in the power-law case, the heating rate can be as high as $H_i\sim0.3$ erg cm$^{-3}$ s$^{-1}$. In terms of a uniform heating rate, this corresponds to a waiting time of $t_N\approx8100$ s. So even for the lowest heating frequency in the uniform case, the heating rate is still much lower. Furthermore, for $t_N=5000$ s, the lowest heating frequency considered here, the loop is allowed to drain to its equilibrium value (as determined by the background heating) between each event such that events with a heating rate $H_0\approx0.2$ erg cm$^{-3}$ s$^{-1}$ are injected into a low-density loop, meaning that the ionization state will not be able to keep pace with the subsequently rapid rise in temperature, resulting in $\mathrm{EM}(T_{eff})$ having a lower temperature cutoff. On the other hand, when the heating events are selected from a power-law distribution, events with $H_i>0.2$ erg cm$^{-3}$ s$^{-1}$ can be injected into a much higher density loop (because lower values of $t_N$ prevent longer draining times). This allows the ionization state to be relatively representative of the electron temperature such that $\mathrm{EM}(T)\approx\mathrm{EM}(T_{eff})$.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively. We select a single sample run from our parameter space in which only the electrons are heated by the events chosen from a power-law distribution of $\alpha=-2.5$ and spaced uniformly by an interval of $t_N=5000$ s. We calculate the resulting $\mathrm{EM}(T)$ and fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$. The left panel of \autoref{fig:em_slope_varying_bounds} shows $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.

@@

	\par\citet{brosius_pervasive_2014}, using observations of an active region from the \textit{EUNIS-13} sounding rocket, found that the intensity ratio of Fe XIX (formed at $T\approx10^{6.95}$ K) to Fe XII (formed at $T\approx10^{6.2}$ K) is $\sim0.59$ inside the AR core as compared to $\sim0.076$ outside, providing possible evidence for impulsive heating. As a proxy for this intensity ratio and an alternative to the hot emission measure slope $b$, we propose using an emission measure ratio, $\mathrm{EM}(T_{hot})/\mathrm{EM}(T_{cool})$. Unlike an emission measure slope, a simple emission measure ratio gives information about the emission at only a single ``hot'' temperature relative to a single ``cool'' temperature. We choose $T_{hot}=10^{6.95}$ K and $T_{cool}=10^{6.3}\approx2\times10^6$ K, the latter slightly higher (closer to $T_{peak}\approx4$ MK) than the formation temperature of Fe XII such that the emission measure ratio is less sensitive to variations in the cool emission and thus a more accurate measure of the amount of hot plasma. 

@@

	\par The emission measure ratio provides a way to compactly compare every point in our multidimensional parameter space while acknowledging that we are reducing $8\times10^4$ s of loop evolution to a single value. The left panel of \autoref{fig:em_ratio_hist_el} shows the case in which only the electrons are heated, where each individual histogram (denoted by linestyle and color) corresponds to a different type of heating function. This means, for example, that the solid blue histogram includes emission measure ratios for all values of $t_N$, but for only those cases where heating events are chosen from a power-law distribution of $\alpha=-1.5$ and $t_{N,i}=t_N$ for all $i$ (i.e. $\beta=0$). We see that the emission measure ratio is largely insensitive to $\alpha$ and is peaked sharply at approximately $0.25$; the distribution peaks at slightly higher values for the $\beta=1$ case though the overall shape of the distribution is the same. Here we have not included the uniform heating case due to small number statistics (i.e. $<20$ emssion measure ratios). The right panel of \autoref{fig:em_ratio_hist_el} shows these same emission measure ratios, but now separated by $t_N$. For example, the solid red histogram includes emission measure ratios for every type of heating function (i.e. uniform, all $\alpha$ and all $\beta$), but for only those runs where $t_N=3000$ s. Note that we choose to only show results for five values of $t_N$ for aesthetic purposes. We find that for $t_N\le3000$ s, the emission measure ratios are largely clustered below 0.5, with $t_N=2000,3000,4000$ s peaking between $\sim0.3-0.45$. For $t_N>4000$ s, the emission measure ratio seems to be more sensitive to the heating frequency .
